%---------------------------------------------------------------------------------------
% Education
%---------------------------------------------------------------------------------------
\newpage
\cvsection{EDUCATION}

\cvmetaevent
{2022 - Current}
{PhD Computational Data}
{Middle TN State Univ. (MTSU)}
{
Specializing in advanced algorithms, data analysis, and deep learning to solve complex problems in diverse industries.\\

Developed and refined predictive models that improved multi classification tasks, contributing to several papers on data optimization and efficiency in NLP, Finance, and HR Resume tracking.
}

\vfill\null
\cvmetaevent
{2007 - 2009}
{MBA Executive}
{Vanderbilt University}
{
Earned an Executive MBA from Vanderbilt University, gaining advanced management training and strategic decision-making skills that have been directly applied to current professional challenges.
}

\vfill\null
\cvmetaevent
{2022 - 2025}
{MS Data Science}
{Middle TN State Univ. (MTSU)}
{
A strong focus on predictive analytics, machine learning, and statistical modeling. Applied comprehensive knowledge to real-world data sets during projects, enhancing predictive accuracy and decision-making capabilities for business applications.
}

\vfill\null
\cvmetaevent
{2002 - 2006}
{BS Computer Engineering \& Science}
{Middle TN State Univ. (MTSU)}
{
B.S. in Computer Engineering and Computer Science from Middle Tennessee State University, graduated with a 3.9 GPA, mastering software development, system architecture, and hardware integration.
}
