%---------------------------------------------------------------------------------------
% Experience
%---------------------------------------------------------------------------------------
\vfill\null
\cvsection{WORK EXPERIENCE}

\cvevent
{2023 - Present}
{Hoehn Innovations, LLC.}
{Owner / Founder}
{At Hoehn Innovations, I work on finding solutions using technology,
process design, and with those tools specializing in creating meaningful hard \& software products for various industries. My role is to contribute technical guidance by conceptualizing and developing innovative solutions to address complex challenges for our clients.}
% Simple Bullets
{\cvlist{
    \item Flutter \& Dart for Mobile Application Development
    \item Vue.JS, Node.JS, PostgreSQL, AWS Full Suite, GCP Firebase
    \item PyTorch \& Torch Lighting Module Design
}}
% Technologies
{} % None
% Achievements
{\cvlist{
    \item Launched Bluetooth device on Amazon with +250 units a month sold
    \item Deployed ML resume scan app to predict employee Turn-over
    \item Tools for RESTful API integration using Pub Sub technologies on AWS
}}


\vfill\null
\cvevent
{2015 - 2022}
{FreightWise, LLC.}
{CTO / CIO / Co-Founder}
{Co-Founded and exited a successful Logistics Technology company providing TMS SaaS \& Managed Transportation services. FreightWise technology optimizes freight profiles and streamlines TMS \& WMS operations.\\[6pt]
In 2019 FreightWise was the 2\textsuperscript{nd} fastest growing company in the US, and the fastest growing company in Nashville four years in a row, 2019-2023.\\[6pt]
Technologies such as Node.JS, PostgreSQL, Docker, AWS, and event-driven programming by use of Kafka delivering real-time web, mobile, and desktop apps.}
{\cvlist{
    \item CTO - Wrote the first lines of code - Exited with 20 developers on staff
    \item Managed Product Mgmt. Team - Applied Pragmatic Marketing principles
    \item Created Customer Solutions Team as an integrated service center withing our SaaS application
    \item Initiated and helped bring to market Cargo Insurance offering within the SaaS platform
}}
{}
{}


\vfill\null
\cvevent
{2015 - 2018}
{Canary Computer Engineering}
{CEO / Co-Founder}
{Architected, designed (hardware \& software), and deployed +300 units at multiple large retailers an event-driven IoT (Internet of Things) platform.\\[6pt]
We used LTE CAT-M1 networks to ensure our devices are the most energy efficient on the market. By integrating a dedicated SSH tunnel between the devices and AWS SQS platform.}
{\cvlist{
    \item Networks using Bluetooth 4.2 \& 5.0 for large range internal applications and LTE CAT-M1 for energy efficient distributed networks.
    \item Develops iOS and Android apps using React Native, ES2015, JAVA, Objective-C, and Swift
}}
{}
{}


\vfill\null
\cvevent
{2012 - 2015}
{Checkpoint Systems}
{Dir. Global Product Management}
{Checkpoint Systems is a global leader in technology solutions for retail, including RFID, EAS (Electronic Article Surveillance), and loss prevention, aimed at improving inventory accuracy and operational efficiency.\\[6pt]I was tasked with completing and deploying a \$2M product to all of North America and Europe in high-end retail stores.}
{\cvlist{
    \item Developed and deployed a \$2M development project for in-store GPS
    \item Traveled extensively to introduce, train, and sell S3i product line I managed
    \item Managed with internal marketing team the successful launch of S3i to numerous USA, Canadian, France, and Netherlands retailers
}}
{}
{}


\vfill\null
\cvevent
{2010 - 2012}
{Griffin Technology}
{EE \& FW Manager}
{
Griffin Technology designed and manufactured technical solutions with an innovative flair. They grew during to become one of the largest providers of accessories for iPhone and Android media. Some of the best known accessories I worked on included the iTrip family of FM transmitters and the groundbreaking Evolve Wireless Sound System.\\[6pt]I managed the electrical and firmware engineering group of 10 members and interacted extensively with the our counterparts in Asia.
}
{\cvlist{
    \item Managed 4 embedded software and firmware developers
    \item Managed 5 electrical and PCB layout engineers
    \item Managed the E-Emissions and Prototype assembly lab and respective technicians
    \item Personally contributed firmware for embedded devices: Bluetooth, TCP/IP, IoT and IR devices
    \item Worked heavily in MySQL and SQL-Server backend IoT applications
}}
{}
{}


\vfill\null
\cvevent
{2007 - 2010}
{Big Time Toys, LLC.}
{Dir. of Manufacturing}
{To ensure on-time development and manufacturing I regularly flew to Asia on a 4-6week basis, logging over 120+ days in-country. This ensured the cultivation of strong relationships with our Asian partners and local development and management team, which enabled the lowering of cost, payment terms, and bringing products faster and more efficiently to market.}
{\cvlist{
    \item Extensive travel to China, Vietnam, and Europe
    \item Manged the development, pricing, and logistics of electronics toys from HKG \& China to the USA and Europe
    \item Worked on establishing manufacturing options in Vietnam as supply chain risk management strategy 
    \item Worked with Walmart, Target, Toys "R" Us, Costco, and numerous European \& Australian retail distribution  
    \item I spent close to 120 days of the year in Asia
}}
{}
{}